Karbowski model in 2-D

### 2020-01-24 paper/briefpaper/brief.tex
Friday afternoon changes

Spatial patterns in neural connectivity provide clues about the constraints
under which brains evolve and develop \citep{purves_iterated_1992}. Perhaps
the most distinctive pattern can be found in the barrel cortex of many rodent
species \cite{woolsey_structural_1970}. The barrels are identifiable soon
after birth in layer 4 of primary somatosensory cortex as dense clusters of
thalamocortical axons, which are enclosed by borders a few neurons thick from
postnatal day 3 \citep{erzurumlu_development_2012}. In the plane tangential to
the cortical surface the barrels constitute a somatotopic map of the whiskers,
with cells within adjacent barrels responding most strongly and quickly to
deflection of adjacent whiskers \citep{armstrong-james_flow_1992}. Barrel
patterning reflects subcortical whisker maps comprising cell aggregates called
barrelettes in the brainstem and barreloids in the thalamus.
%\cite{van_der_loos_barreloids_1976}.

Barrel formation requires afferent input from whisker stimulation and thalamic
calcium waves \citep{anton-bolanos_prenatal_2019}, and depends on a complex
network of axon guidance molecules such as ephrin-A5 and A7 and adhesion
molecules such as cadherin-6 and 8
\citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}.  This network
is orchestrated by interactions between morphogens Fgf8 and Fgf17 and
transcription factors Emx2, Pax6, Sp8, and Coup-tf1
\citep{shimogori_fibroblast_2005}, which are expressed in gradients that mark
orthogonal axes and can be manipulated to stretch, shrink, shift, and even
duplicate barrels \cite{assimacopoulos_fibroblast_2012}.
% Removed ref: ,bishop_regulation_2000 after ..Coup-tf1

The barrel boundaries form a Voronoi tessellation across the cortical sheet
\citep{senft_mouse_1991} (Fig.\,1A), suggesting that barreloid topology is
preserved in the projection of thalamocortical axons into the cortex, and that
a barrel forms by lateral axon branching from an initial centre-point that
ceases upon contact with axons branching from adjacent centres.  \cmnt{Another
  sentence about center-points here.} But the assumption of pre-arranged
centres is difficult to resolve with the observation that axons arrive in the
cortical plate as an undifferentiated bundle, prior to barreloid formation
\cite{agmon_organized_1993}.

Alternatively, reaction-diffusion dynamics could generate a Voronoi
tessellation without pre-arranged centres, by amplifying characteristic modes
in a noisy initial distribution of axon branches, as a net effect of
short-range cooperative and longer-range competitive
interactions. Accordingly, the barrel pattern would be determined by the
relative strength of these interactions and by the shape of the cortical field
boundary. However, intrinsic cortical dynamics alone cannot account for the
topographic correspondence between thalamic and cortical domains, the
irregular sizes and specific arrangement of the barrels in rows and arcs, or
the influence of gene expression gradients.

The centre-point and reaction-diffusion models are not mutually
exclusive. Pre-organised centres could bias reaction-diffusion processes to
generate specific arrangements more reliably, and mechanisms of lateral axon
branching may constitute the tension between cooperation and competition
required for self-organization. However, proof that barrel patterning can
emerge from an undifferentiated bundle of axons, based only on local
interactions, would show that a separate stage and/or extrinsic mechanism for
pre-organising thalamocortical connections need not be assumed. To this end,
we ask whether barrel maps can emerge in a system with reaction-diffusion
dynamics, under the guidance of signalling gradients, and in the absence of
pre-defined centres.

@@

Karbowski \& Ermentrout \citep{karbowski_model_2004} developed a
reaction-diffusion style model of how extrinsic signalling gradients can
constrain the emergence of distinct fields from intrinsic cortical
dynamics. Their model defines how the density of connections $c(x,t)$ and axon
branches $a(x,t)$ interact at time $t$, along a 1D anterior-posterior axis
$x$, for $N$ thalamocortical projections indexed by $i$. The model was derived
from the assumption that the rates at which $a_i$ and $c_i$ grow are
reciprocally coupled. Extending the original 1D model to simulate arealization
on a 2D cortical sheet, we use $a_i(\mb{x},t)$ and $c_i(\mb{x},t)$, and model
synaptogenesis as
%
\begin{equation} \label{eq:dc}
\frac{\partial c_i}{\partial t} =-\alpha c_i +\beta  \left(1 - \sum_{j=1}^{N} c_{j}\right)[a_i]^k.
\end{equation}
%
Accordingly, where the total density of synaptic connections sums to one,
connections decay at rate $\alpha$. Otherwise the connection density increases
non-linearly ($k>1$) with the density of axon branching. Axon branching is
modelled as
%
\begin{equation} \label{eq:da}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right) - \frac{\partial c_i}{\partial t} + \chi_i.
\end{equation}
%
The first term on the right describes the divergence (indicated by
$\nabla\vcdot$) of the quantity in parentheses, which is referred to as the
`flux' of axonal branching. The flux represents diffusion across the cortical
sheet, at rate $D$, and the influence of $M$ molecular signalling fields,
$\rho(\mb{x})$. The influence of a given field (indexed by $j$) on a given
thalamic projection (indexed by $i$), is determined by $\gamma_{i,j}$, which
may be positive or negative in order that axons may branch in the direction of
either higher or lower concentrations. The second term on the right represents
an assumption that axon branching decreases when synaptogenesis increases, and
vice versa, i.e., \cmnt{when a connection is made, the axon branching
  decreases by one branch and when a connection is lost, one branch is added
  to the branching density}
%that axon branches are required for synaptic connections to form.
Here $\chi_i=0$ is a placeholder.

@@

\begin{figure}
\begin{fullwidth}
\includegraphics[width=\linewidth]{./MainFig_superlowres.png}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
  by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
  measure departure (Honda-$\delta$; see \cite{senft_mouse_1991}) from a
  perfect Voronoi tesselation. Right shows the initial distribution of axon
  branching density ($a$) for one thalamocortical projection, and two
  molecular guidance fields ($\rho$). \textbf{B} The strengths of interaction
  $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
  projections by the lengths of green and blue arrows respectively, assuming
  that similar fields aligned to the posterior-anterior and medial-lateral
  axes in the ventroposterior medial nucleus of the thalamus are sampled at
  the locations of putative barreloid centers (reconstructed from
  \cite{haidarliu_size_2001}). \textbf{C} Simulation results for parameters
  $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$,
  $\epsilon=150$ and $\delta{t}=0.0001$. Colours indicate the thalamic
  projection for which the connection density is maximal, black lines
  delineate boundaries, and overlaid contours show $c>0.5$ (see Movie
  S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from
  simulation approaching that obtained from barrels in \textbf{A} (dotted
  line); black squares measure the correspondence between the real and
  simulated barrel shapes, $\eta$ (the product of the sum of squared
  differences between real and simulated centers and the sum of differences in
  area; units mm$^4$). \textbf{E} Guidance fields and emergent barrel pattern
  in a Fgf8 misexpression experiment
  (c.f. \cite{assimacopoulos_fibroblast_2012}), simulated by reflecting
  $\rho_1$ at the join ($\epsilon=80$). All scale bars 1mm.}
\label{fig:main}
\end{fullwidth}
\end{figure}

@@

The term in parentheses in Eq.~\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching we
redefined
%
\begin{equation} \label{eq:comp}
\chi_i(\mb{x}, t) = - \frac{\epsilon  a_i}{N-1} \sum_{j \ne i}^{N} a_{j},
\end{equation}
%
which reduces branching for each projection where the branches of other
projections are dense. Divisive normalization keeps the axon branch density
bounded on each iteration to the initial density at $t=0$;
%
\begin{equation} \label{eq:norm}
  a_i(\mathbf{x}, t) = \oiint_{S}  a_i(\mathbf{x}, 0) \dif S \; \frac {a'_i(\mathbf{x}, t)} {\oiint_{S}
  a'_i(\mathbf{x}, t) \dif S}
\end{equation}
%
where prime symbols indicate the use of intermediate values computed from
Eqs.~\ref{eq:dc}--\ref{eq:comp} at time $t-{\delta}t$. \cmnt{Normalization
  corresponds to the biological constraint that the branching and growth of
  thalamocortical axons is backed by a finite resource provided by their
  parent cell bodies.}

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that a projection interacts with a given ephrin field in
the cortical subplate with a strength determined by the concentration of a
similar molecule at its thalamic origin, i.e., the putative barreloid
center. As such, two orthogonal linear thalamic gradients were defined, from
which 41 pairs of $\gamma$ values were sampled, at the coordinates of 41
barreloid centers recreated from \cite{haidarliu_size_2001} (Fig.\,1B).

A cortical boundary enclosing 41 corresponding barrels was traced from a
cytochrome oxidase stain from \cite{zheng_signal_2001}, and
Eqs.~\ref{eq:dc}--\ref{eq:norm} were solved for $N=41$ projections on the
resulting domain, using $M=2$ linear signalling gradients aligned with the
anterior-posterior and medial-lateral axes. From random initial conditions for
$a({\bf x},0)$ and $c({\bf x},0)$, a clear Voronoi-like tesselation emerged
(Fig.\,1C; see Movie S1). A reduction in the Honda delta metric (see
\cite{senft_mouse_1991}) confirmed that a `good' Voronoi pattern emerged
within $\approx 3000$ iterations (see Fig.\,1D). A measure of the difference
in shape between real and simulated barrels revealed a strong correspondence
(see Fig.\,1D).

To further investigate the interplay of genetic and intrinsic mechanisms we
simulated a seminal barrel duplication experiment
\cite{shimogori_fibroblast_2005}, first by solving on a cortical domain
comprising two separate, identically shaped cortical boundaries. In this case
one distinct cortical field per thalamic projection emerged, within one of the
two boundaries only, i.e., no duplication. However, merging the two fields to
create an extended mirror-symmetric boundary shape, with an anterior-posterior
guidance field reflected at the join, gave rise to two mirror-symmetrical
barrel fields comprising 2N barrels, i.e., two cortical fields for each
thalamic projection (Fig.\,1E). Together these results suggest that by the
misexpression of Fgf8, Shimogori \& Grove \citep{shimogori_fibroblast_2005}
effectively created one large barrel field rather than two distinct cortical
fields.

@@

Moreover, the present results confirm that somatotopic map formation does not
require the pre-specification of centre-points by as yet undetermined
additional developmental mechanisms.

>>>>

Spatial patterns in neural connectivity provide clues about the constraints
under which brains evolve and develop \citep{purves_iterated_1992}. Perhaps
the most distinctive pattern can be found in the barrel cortex of many rodent
species \citep{woolsey_structural_1970}. The barrels are identifiable soon
after birth in layer 4 of primary somatosensory cortex as dense clusters of
thalamocortical axons, which are enclosed by borders a few neurons thick from
postnatal day 3 \citep{erzurumlu_development_2012}. In the plane tangential to
the cortical surface the barrels constitute a somatotopic map of the whiskers,
with cells within adjacent barrels responding most strongly and quickly to
deflection of adjacent whiskers \citep{armstrong-james_flow_1992}. Barrel
patterning reflects subcortical whisker maps comprising cell aggregates called
barrelettes in the brainstem and barreloids in the thalamus
\citep{ma_barrelettesarchitectonic_1991,van_der_loos_barreloids_1976}.

Barrel formation requires afferent input from whisker stimulation and thalamic
calcium waves \citep{anton-bolanos_prenatal_2019}, and depends on a complex
network of axon guidance molecules such as ephrin-A5 and A7 and adhesion
molecules such as cadherin-6 and 8
\citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}.  This network
is orchestrated by interactions between morphogens Fgf8 and Fgf17 and
transcription factors Emx2, Pax6, Sp8, and Coup-tf1
\citep{shimogori_fibroblast_2005,bishop_regulation_2000}, which are expressed
in gradients that mark orthogonal axes and can be manipulated to stretch,
shrink, shift, and even duplicate barrels
\citep{assimacopoulos_fibroblast_2012}.

The barrel boundaries form a Voronoi tessellation across the cortical sheet
\citep{senft_mouse_1991} (Fig.\,1A), suggesting that barreloid topology is
preserved in the projection of thalamocortical axons into the cortex, and that
a barrel forms by lateral axon branching from an initial center-point that
ceases upon contact with axons branching from adjacent centers.  The
assumption of pre-arranged center-points \cmnt{(an assumption shared with
  chemoaffinity theories following \citealp{sperry_chemoaffinity_1963})} is
difficult to resolve with the observation that axons arrive in the cortical
plate as an undifferentiated bundle, \emph{prior} to barreloid formation
\citep{agmon_organized_1993}.  \cmnt{But it's not that hard to resolve, if, as
  in the paper, we assume orthogonal gradients in the barreloid field.}

% Note: The key difference between this theory and the chemospecificity theory
% is that of group membership.

Alternatively, reaction-diffusion dynamics could generate a Voronoi
tessellation without pre-arranged centers, by amplifying characteristic modes
in a noisy initial distribution of axon branches, as a net effect of
short-range cooperative and longer-range competitive
interactions. Accordingly, the barrel pattern would be determined by the
relative strength of these interactions and by the shape of the cortical field
boundary. However, intrinsic cortical dynamics alone cannot account for the
topographic correspondence between thalamic and cortical domains, the
irregular sizes and specific arrangement of the barrels in rows and arcs, or
the influence of gene expression gradients.

The center-point and reaction-diffusion models are not mutually
exclusive. Pre-organised centers could bias reaction-diffusion processes to
generate specific arrangements more reliably, and mechanisms of lateral axon
branching may constitute the tension between cooperation and competition
required for self-organization. However, proof that barrel patterning can
emerge from an undifferentiated bundle of axons, based only on local
interactions, would show that a separate stage and/or extrinsic mechanism for
pre-organising thalamocortical connections need not be assumed. To this end,
we ask whether barrel maps can emerge in a system with reaction-diffusion
dynamics, under the guidance of signalling gradients, and in the absence of
pre-defined centers.

@@

\cite{karbowski_model_2004} developed a reaction-diffusion style model of how
extrinsic signalling gradients can constrain the emergence of distinct fields
from intrinsic cortical dynamics. Their model defines how the density of
connections $c(x,t)$ and axon branches $a(x,t)$ interact at time $t$, along a
1D anterior-posterior axis $x$, for $N$ thalamocortical projections indexed by
$i$. The model was derived from the assumption that the rates at which $a_i$
and $c_i$ grow are reciprocally coupled. Extending the original 1D model to
simulate arealization on a 2D cortical sheet, we use $a_i(\mb{x},t)$ and
$c_i(\mb{x},t)$, and model synaptogenesis as
%
\begin{equation} \label{eq:dc}
\frac{\partial c_i}{\partial t} =-\alpha c_i +\beta  \left(1 - \sum_{j=1}^{N} c_{j}\right)[a_i]^k.
\end{equation}
%
Accordingly, where the total density of synaptic connections sums to one,
connections decay at rate $\alpha$. Otherwise the connection density increases
non-linearly ($k>1$) with the density of axon branching. Axon branching is
modelled as
%
\begin{equation} \label{eq:da}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right) - \frac{\partial c_i}{\partial t} + \chi_i.
\end{equation}
%
The first term on the right describes the divergence (indicated by
$\nabla\vcdot$) of the quantity in parentheses, which is referred to as the
`flux' of axonal branching. The flux represents diffusion across the cortical
sheet, at rate $D$, and the influence of $M$ molecular signalling fields,
$\rho(\mb{x})$. The influence of a given field (indexed by $j$) on a given
thalamic projection (indexed by $i$), is determined by $\gamma_{i,j}$, which
may be positive or negative in order that axons may branch in the direction of
either higher or lower concentrations. The second term on the right represents
an assumption that axon branching decreases when synaptogenesis increases, and
vice versa, i.e., \cmnt{when a connection is made, the axon branching
  decreases by one branch and when a connection is lost, one branch is added
  to the branching density}
%that axon branches are required for synaptic connections to form.
Here $\chi_i=0$ is a placeholder.

@@

\begin{figure}
\begin{fullwidth}
\includegraphics[width=\linewidth]{./MainFig_superlowres.png}
\caption{\textbf{A} Left shows a cytochrome oxidase stain obtained from rat S1
  by \cite{zheng_signal_2001}, with black lines to delineate barrels and to
  measure departure (Honda-$\delta$; see \citealp{senft_mouse_1991}) from a
  perfect Voronoi tesselation. Right shows the initial distribution of axon
  branching density ($a$) for one thalamocortical projection, and two
  molecular guidance fields ($\rho$). \textbf{B} The strengths of interaction
  $\gamma$ with fields $\rho_1$ and $\rho_2$ are indicated for each of 41
  projections by the lengths of green and blue arrows respectively, assuming
  that similar fields aligned to the posterior-anterior and medial-lateral
  axes in the ventroposterior medial nucleus of the thalamus are sampled at
  the locations of putative barreloid centers (reconstructed from
  \citealp{haidarliu_size_2001}). \textbf{C} Simulation results for parameters
  $N=41$, $\alpha=3$, $\beta=20$, $k=3$, $D=0.2$, $\gamma\in\pm 2$,
  $\epsilon=150$ and $\delta{t}=0.0001$. Colours indicate the thalamic
  projection for which the connection density is maximal, black lines
  delineate boundaries, and overlaid contours show $c>0.5$ (see Movie
  S1). \textbf{D} Red dots show the Honda-$\delta$ metric obtained from
  simulation approaching that obtained from barrels in \textbf{A} (dotted
  line); black squares measure the correspondence between the real and
  simulated barrel shapes, $\eta$ (the product of the sum of squared
  differences between real and simulated centers and the sum of differences in
  area; units mm$^4$). \textbf{E} Guidance fields and emergent barrel pattern
  in a Fgf8 misexpression experiment
  (c.f. \citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
  $\rho_1$ at the join ($\epsilon=80$). All scale bars 1mm.}
\label{fig:main}
\end{fullwidth}
\end{figure}

@@

The term in parentheses in Eq.~\ref{eq:dc} represents competition between
thalamocortical projections for a limited availability of cortical
connections. To introduce competition also in terms of axon branching we
redefined
%
\begin{equation} \label{eq:comp}
\chi_i(\mb{x}, t) = - \frac{\epsilon  a_i}{N-1} \sum_{j \ne i}^{N} a_{j},
\end{equation}
%
which reduces branching for each projection where the branches of other
projections are dense. Divisive normalization keeps the axon branch density
bounded on each iteration to the initial density at $t=0$ \cmnt{(less the
  number of connections that have been made).};
%
\begin{equation} \label{eq:norm}
  a_i(\mathbf{x}, t) = \oiint_{S} \big[ a_i(\mathbf{x}, 0) - c_i(\mathbf{x}, t) \big] \dif S \; \frac {a'_i(\mathbf{x}, t)} {\oiint_{S}
  a'_i(\mathbf{x}, t) \dif S}
\end{equation}
%
where prime symbols indicate the use of intermediate values computed from
Eqs.~\ref{eq:dc}--\ref{eq:comp} at time $t-{\delta}t$. \cmnt{Normalization
  corresponds to the biological constraint that the branching and growth of
  thalamocortical axons is backed by a finite resource provided by their
  parent cell bodies.}

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that a projection interacts with a given ephrin field in
the cortical subplate with a strength determined by the concentration of a
similar molecule at its thalamic origin, i.e., the putative barreloid
center. As such, two orthogonal linear thalamic gradients were defined, from
which 41 pairs of $\gamma$ values were sampled, at the coordinates of 41
barreloid centers recreated from \citealp{haidarliu_size_2001} (Fig.\,1B).

A cortical boundary enclosing 41 corresponding barrels was traced from a
cytochrome oxidase stain from \cite{zheng_signal_2001}, and
Eqs.~\ref{eq:dc}--\ref{eq:norm} were solved for $N=41$ projections on the
resulting domain, using $M=2$ linear signalling gradients aligned with the
anterior-posterior and medial-lateral axes. From random initial conditions for
$a({\bf x},0)$ and $c({\bf x},0)$, a clear Voronoi-like tesselation emerged
(Fig.\,1C; see Movie S1). A reduction in the Honda delta metric (see
\citealp{senft_mouse_1991}) confirmed that a `good' Voronoi pattern emerged
within $\approx 3000$ iterations (see Fig.\,1D). A measure of the difference
in shape between real and simulated barrels revealed a strong correspondence
(see Fig.\,1D).

To further investigate the interplay of genetic and intrinsic mechanisms we
simulated a seminal barrel duplication experiment
\citep{shimogori_fibroblast_2005}, first by solving on a cortical domain
comprising two separate, identically shaped cortical boundaries. In this case
one distinct cortical field per thalamic projection emerged, within one of the
two boundaries only, i.e., no duplication. However, merging the two fields to
create an extended mirror-symmetric boundary shape, with an anterior-posterior
guidance field reflected at the join, gave rise to two mirror-symmetrical
barrel fields comprising 2N barrels, i.e., two cortical fields for each
thalamic projection (Fig.\,1E). Together these results suggest that by the
misexpression of Fgf8, \cite{shimogori_fibroblast_2005}
effectively created one large barrel field rather than two distinct cortical
fields.

@@

Moreover, the present results confirm that somatotopic map formation does not
require the pre-specification of center-points by as yet undetermined
additional developmental mechanisms.

### 2020-01-24 paper/supplementary/supp.tex
Friday afternoon changes

One further extension is to note that in the K\&E simulation, the quantity of
axon branching in the system is bounded and the number of connections and
branching quantity is related. So we could normalize the `proportion of $a_i$
which is not participating in connections'.
%
\begin{equation}\label{eq:norm_comp8plus2}
        a_i[j](t)' = \sum_j^{n_e} \big[ a_i[j](0) - c_i[j](t) \big] \; \frac {a_i[j](t)} {\textstyle \sum_j^{n_e} a_i[j](t) }
\end{equation}
%
The continuous equivalent, if the surface is called $S$, would be:
%
\begin{equation} \label{eq:norm_comp8plus3}
  a_i(\mathbf{x}, t) = \oiint_{S} \big[  a_i(\mathbf{x}, 0) - c_i(\mathbf{x},
  t) \big]  dS \; \frac {a'_i(\mathbf{x}, t)} {\oiint_{S}
  a'_i(\mathbf{x}, t) dS}
\end{equation}

>>>>

One further extension is to note that in the K\&E simulation, the quantity of
axon branching in the system is bounded and the number of connections and
branching quantity is related. So we could normalize the `proportion of $a_i$
which is not participating in connections'.
%
\begin{equation}\label{eq:norm_comp8plus2}
        a_i[j](t)' = \sum_j^{n_e} \big[ a_i[j](0) - c_i[j](t) \big] \; \frac {a_i[j](t)} {\textstyle \sum_j^{n_e} a_i[j](t) }
\end{equation}
%
The continuous equivalent, if the surface is called $S$, would be:
%
\begin{equation} \label{eq:norm_comp8plus3}
\begin{split}
  a_i(\mathbf{x}, t) & = \oiint_{S} \big[  a_i(\mathbf{x}, 0) - c_i(\mathbf{x},
  t) \big]  dS \; \frac {a'_i(\mathbf{x}, t)} {\oiint_{S}
  a'_i(\mathbf{x}, t) dS} \\
  & = \bigg[ \oiint_{S} a_i(\mathbf{x}, 0) dS - \oiint_{S} c_i(\mathbf{x}, t)
  dS  \bigg] \; \frac {a'_i(\mathbf{x}, t)} {\oiint_{S}
  a'_i(\mathbf{x}, t) dS}
\end{split}
\end{equation}
which is a little more expensive as $\oiint_{S} c_i(\mathbf{x}, t) dS$ has to
be computed on each iteration.
